\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.8in}
\addtolength{\evensidemargin}{-0.8in}
\addtolength{\textwidth}{1.6in}
\addtolength{\topmargin}{-0.9in}
\addtolength{\textheight}{1.7in}
\setlength{\footskip}{12pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1.25pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3.25pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0.75pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=-0.25pt, parsep=0.5pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2.5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \Huge {Harsh Devisha} \\ \vspace{5pt}
  \small {\href{https://www.harshdevisha.com}{\underline{harshdevisha.com}} $|$ +1-310-696-9659 $|$ \href{mailto:harshdevisha91@gmail.com}{\underline{harshdevisha91@gmail.com}} $|$ \href{https://www.linkedin.com/in/harsh-devisha/}{\underline{linkedin.com/in/harsh-devisha}} }

\end{center}
\vspace{-5mm}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Loyola Marymount University - 3.9/4.0}{Los Angeles, CA}
      {Master of Science in Computer Science}{January 2024 -- December 2025}

    \resumeSubheading
      {Pandit Deendayal Petroleum University}{Gandhinagar, GJ}
      {Bachelor of Technology in Electrical Engineering}{June 2017 -- June 2021}
  \resumeSubHeadingListEnd

%-----------RELEVANT COURSEWORK-----------
\section{Relevant Coursework}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
         \textbf{Core Systems}{: Operating Systems, Distributed Systems, Computer Networks, Database Management Systems} \\
         \textbf{Advanced Computing}{: Compiler Construction, Advanced Algorithms, Theory of Computation} \\
         \textbf{Specialized}{: Network Programming, Parallel Computing, System Security}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Graduate Research Assistant}{August 2025 -- Present}
      {\href{https://research.kubishi.com/}{\underline{Kubishi}} $|$ \underline{LMU Seaver School of Science and Engineering}}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Analyzed the mathematics of a variant of pure-pursuit problem with potential failure.}
        \resumeItem{Analyzed the online and optimal-offline strategies for competitive ratio and proved the worst-case failure scenario.}
        \resumeItem{Used Python for simulation and Mathematica to verify proof rigour}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{December 2024 -- May 2025}
      {\underline{SetFindr}}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Implmented JWT authentication and RESTful APIs using Python FastAPI and Node.js.}
        \resumeItem{Implemented vector search using Qdrant achieving sub-100ms query latency on 10K+ embeddings.}
        \resumeItem{Integrated Google Cloud APIs for OAuth2 authentication and geospatial features.}
        \resumeItem{Built unstructured-document processing pipelines using OpenAI API for search and recommendation.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Specialist}{August 2024 -- May 2025}
      {\href{https://careers.lmu.edu/}{\underline{LMU Career and Professional Development Department}}}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Built ETL pipelines to handle daily appointment and engagement datasets.}
        \resumeItem{Identified engagement patterns, contributing to a $200\%$ increase in participation from under-represented demographics.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer - I}{December 2021 -- December 2023}
      {\href{https://nexuslinkservices.com/}{\underline{Nexuslink Services}}}{Ahmedabad, GJ}
      \resumeItemListStart
        \resumeItem{Automated complex document generation using headless browser (Puppeteer), saving over $100$ operational hours monthly.}
        \resumeItem{Created standardized API client abstraction with centralized error handling and retry logic, reducing boilerplate by $50+$ LOC per endpoint.}
        \resumeItem{Implemented authentication utilizing JWT with session management and refresh token rotation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Zue (Distributed Log)} $|$ \emph{Zig}}{\href{https://github.com/lostcache/zue}{\underline{github}}}
      \resumeItemListStart
        \resumeItem{Built distributed storage engine in Zig implementing Raft-like consensus with quorum-based replication, automatic leader-driven log repair, and ISR tracking.}
        \resumeItem{Implemented log-structured storage with segmented append-only architecture and sparse indexing, maintaining O(1) write complexity.}
        \resumeItem{Implemented non-blocking event-loop to handle client requests, replication and background repair.}
        \resumeItem{Designed and Implemented Binary Serialization Format for communication between nodes.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Sparrow Language Interpreter} $|$ \emph{Java, Compiler Design}}{\href{https://github.com/lostcache/sparrow-interpreter}{\underline{github}}}
      \resumeItemListStart
        \resumeItem{Built interpreter for instruction-based DSL with lexer, parser, and runtime engine.}
        \resumeItem{Implemented recursive descent parser for typechecking and AST generation and used visitor pattern for runtime execution.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  %-----------TECHNICAL SKILLS-----------
  \section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Programming Languages}{: C++, Python, Rust, Java, JavaScript/TypeScript, Go, OCaml} \\
      \textbf{Backend}{: Node.js, FastAPI, RESTful APIs} \\
      \textbf{Cloud Platforms}{: AWS (EC2, S3), Google Cloud (Maps API, OAuth2)} \\
      \textbf{Databases}{: PostgreSQL, MongoDB, Redis, Qdrant (Vector DB)} \\
      \textbf{Project Management}{: Jira, Click-Up, Scrum, Agile}
    }}
  \end{itemize}

\end{document}
